---
title: "Results from the Code Sharing Survey"
author: |
  | Benjamin Chan (chanb@ohsu.edu)
  | Center for Health Systems Effectiveness
date: "September 25, 2015"
output:
  ioslides_presentation:
    fig_width: 10
    keep_md: yes
    widescreen: yes
---


## Tidy data

* [SurveyMonkey](https://www.surveymonkey.com) data file was downloaded on 9/17/2015

* Unzip the downloaded file

```{r, echo=FALSE, results='hide'}
f <- file.path(getwd(), "Data_All_150917.zip")
unzip(f, list=TRUE)
unzip(f, exdir=tempdir())
list.files(file.path(tempdir(), "CSV"))
```

* Read CSV file into `r R.Version()$version.string`

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
library(data.table, quietly=TRUE)
library(bit64, quietly=TRUE)
f <- file.path(tempdir(), "CSV", "Sheet_1.csv")
D <- fread(f, header=FALSE, na.strings=c("NA", ""), skip=2, drop=2:9, stringsAsFactors=FALSE)
setnames(D,
         names(D),
         c("id",
           "Interest1",
           "Interest2",
           "Interest3",
           "Interest4",
           "Interest5",
           "Interest6",
           "Interest7",
           "CurrentUse1",
           "CurrentUse2",
           "CurrentUse3",
           "CurrentUse4",
           "CurrentUse5",
           "CurrentUse6",
           "CurrentUse7",
           "CurrentUse8",
           "CurrentUse9",
           "CurrentUse10",
           "CurrentUseGithub",
           "Security1",
           "Security2",
           "Security3",
           "Security4",
           "WouldUse1",
           "WouldUse2",
           "WouldUse3",
           "WouldUse4",
           "WouldUse5",
           "DiscussFurther",
           "Concerns",
           "Learn",
           "OtherGroups",
           "Contact"))        
```

* Factorize some responses

```{r, echo=FALSE, results='hide'}
D[,
  CurrentUseGithub := factor(CurrentUseGithub,
                             levels=c("I have an account on Github but use it sparingly",
                                      "I have an account and Github is my go-to spot for code",
                                      "I know of Github but am not a current user"),
                             labels=c("Have account, use sparingly",
                                      "Have account, my go-to",
                                      "No account, not a user"))]
D[,
  DiscussFurther := factor(DiscussFurther,
                         labels=c("Yes",
                                  "YES!!!",
                                  "Somewhat"))]
```

* Recode *check all that apply* responses from character to integer

```{r, echo=FALSE, results='hide'}
D[,
  `:=` (Interest1 = as.integer(!is.na(Interest1)),
        Interest2 = as.integer(!is.na(Interest2)),
        Interest3 = as.integer(!is.na(Interest3)),
        Interest4 = as.integer(!is.na(Interest4)),
        Interest5 = as.integer(!is.na(Interest5)),
        Interest6 = as.integer(!is.na(Interest6)),
        Interest7 = as.integer(!is.na(Interest7)),
        CurrentUse1  = as.integer(!is.na(CurrentUse1 )),
        CurrentUse2  = as.integer(!is.na(CurrentUse2 )),
        CurrentUse3  = as.integer(!is.na(CurrentUse3 )),
        CurrentUse4  = as.integer(!is.na(CurrentUse4 )),
        CurrentUse5  = as.integer(!is.na(CurrentUse5 )),
        CurrentUse6  = as.integer(!is.na(CurrentUse6 )),
        CurrentUse7  = as.integer(!is.na(CurrentUse7 )),
        CurrentUse8  = as.integer(!is.na(CurrentUse8 )),
        CurrentUse9  = as.integer(!is.na(CurrentUse9 )),
        CurrentUse10 = as.integer(!is.na(CurrentUse10)),
        Security1 = as.integer(!is.na(Security1)),
        Security2 = as.integer(!is.na(Security2)),
        Security3 = as.integer(!is.na(Security3)),
        Security4 = as.integer(!is.na(Security4)),
        WouldUse1 = as.integer(!is.na(WouldUse1)),
        WouldUse2 = as.integer(!is.na(WouldUse2)),
        WouldUse3 = as.integer(!is.na(WouldUse3)),
        WouldUse4 = as.integer(!is.na(WouldUse4)),
        WouldUse5 = as.integer(!is.na(WouldUse5)))]
```

* Reshaped data table from wide to long

```{r, echo=FALSE, results='hide'}
library(reshape2)
isCheckbox <- 1:ncol(D)
isCheckbox <- isCheckbox[sapply(D, class) == "integer"]
DCheckbox <- melt(D, id.vars="id", measure.vars=isCheckbox)
```

* Add `question` string

```{r, echo=FALSE, results='hide'}
DCheckbox[grep("Interest", variable),
          question := "How much interest do you have in a common OHSU repository for code, either as a way to share your code or a resource when you are looking for ideas or methods?"]
DCheckbox[grep("CurrentUse", variable),
          question := "Do you use any of the following code sharing platforms?"]
DCheckbox[grep("Security", variable),
          question := "With which level(s) of security in code-sharing would you be comfortable?"]
DCheckbox[grep("WouldUse", variable),
          question := "If OHSU were to set up a code base comprising Github repositories with appropriate security, how likely would you be to use it?"]
```

* Factorize `variable`

```{r, echo=FALSE, results='hide'}
levels <- c("Interest1",
            "Interest2",
            "Interest3",
            "Interest4",
            "Interest5",
            "Interest6",
            "Interest7",
            "CurrentUse1",
            "CurrentUse2",
            "CurrentUse3",
            "CurrentUse4",
            "CurrentUse5",
            "CurrentUse6",
            "CurrentUse7",
            "CurrentUse8",
            "CurrentUse9",
            "CurrentUse10",    
            "Security1",
            "Security2",
            "Security3",
            "Security4",
            "WouldUse1",
            "WouldUse2",
            "WouldUse3",
            "WouldUse4",
            "WouldUse5")
labels <- c("Do not code",
            "Not interested in uploading",
            "Not interested in downloading",
            "Might upload",
            "Might download",
            "Upload regularly",
            "Download regularly",
            "Looking over shoulder",
            "Email",
            "SharePoint",
            "Portable media",
            "Multi-user machines",
            "X:\ drive",
            "box.com",
            "CVS, SVN or other VCS",
            "Github",
            "Other",    
            "Not sure",
            "Enterprise, inside OHSU firewall",
            "Private, publicly hosted",
            "Public",
            "Would not use OHSU Github",
            "Would upload occasionally",
            "Would download occasionally",
            "Would upload regularly",
            "Would download regularly")
DCheckbox[, variable := factor(variable, levels=levels, labels=labels)]
```

* See the code [here](makeSlides.Rmd)


## How much interest do you have in a common OHSU repository for code?

```{r, echo=FALSE}
# url <- "https://gist.githubusercontent.com/benjamin-chan/3d569db12bb223e8b3c4/raw/2fb6124218cef53484a320d1a91fcc7ef13436dc/colorPalette.R"
# source(url)
colorPalette <- function () {
  c(rgb(  1,  67, 134, maxColorValue=255),
    rgb(119, 120, 123, maxColorValue=255),
    rgb(139, 184, 234, maxColorValue=255),
    rgb(188, 190, 192, maxColorValue=255),
    rgb( 94, 122, 162, maxColorValue=255),
    rgb(223, 122,  28, maxColorValue=255))
}
plotLogical <- function(D) {
  require(ggplot2, quietly=TRUE)
  G <- ggplot(D)
  G <- G + aes(x=variable, fill=factor(-value))
  G <- G + geom_bar()
  G <- G + scale_fill_manual("",
                             labels=c("Checked", "Unchecked"),
                             values=colorPalette())
  G <- G + scale_x_discrete("")
  G <- G + scale_y_continuous("Number of responses")
  G <- G + coord_flip()
  G
}
```

```{r, echo=FALSE}
plotLogical(DCheckbox[grep("How much interest", question)])
```


## Do you use any of the following code sharing platforms?

```{r, echo=FALSE}
plotLogical(DCheckbox[grep("Do you use", question)])
```


## To get specific, are you a Github user?

```{r, echo=FALSE}
G <- ggplot(D)
G <- G + aes(x=CurrentUseGithub, fill=CurrentUseGithub)
G <- G + geom_bar()
G <- G + scale_fill_manual("", values=colorPalette())
G <- G + scale_x_discrete("")
G <- G + scale_y_continuous("Number of responses")
G <- G + coord_flip()
G <- G + theme(legend.position="none")
G
```


## With which level(s) of security in code-sharing would you be comfortable?

```{r, echo=FALSE}
plotLogical(DCheckbox[grep("With which level", question)])
```


## If OHSU were to set up a code base comprising Github repositories with appropriate security, how likely would you be to use it?

```{r, echo=FALSE}
plotLogical(DCheckbox[grep("Github", question)])
```


## Are you interested in further discussion of code sharing at OHSU?

```{r, echo=FALSE}
G <- ggplot(D)
G <- G + aes(x=DiscussFurther, fill=DiscussFurther)
G <- G + geom_bar()
G <- G + scale_fill_manual("", values=colorPalette())
G <- G + scale_x_discrete("")
G <- G + scale_y_continuous("Number of responses")
G <- G + coord_flip()
G <- G + theme(legend.position="none")
G
```


## Please share any concerns you've had with code sharing

```{r, echo=FALSE}
n <- length(D[!is.na(Concerns), Concerns])
concerns <- D[!is.na(Concerns), Concerns][order(sample(1:n))]
```

1. `r concerns[1]`
1. `r concerns[2]`
1. `r concerns[3]`
1. `r concerns[4]`
1. `r concerns[5]`

## Any concerns...

1. `r concerns[6]`
1. `r concerns[7]`
1. `r concerns[8]`
1. `r concerns[9]`

## Any concerns...

1. `r concerns[10]`
1. `r concerns[11]`
1. `r concerns[12]`
1. `r concerns[13]`


## What are some things you'd like to learn about Github?

```{r, echo=FALSE, results='asis'}
n <- length(D[!is.na(Learn), Learn])
learn <- D[!is.na(Learn), Learn][order(sample(1:n))]
```

1. `r learn[1]`
1. `r learn[2]`
1. `r learn[3]`
1. `r learn[4]`
1. `r learn[5]`

## Some things you'd like to learn... ?

1. `r learn[6]`
1. `r learn[7]`
1. `r learn[8]`
1. `r learn[9]`

## Some things you'd like to learn... ?

1. `r learn[10]`
1. `r learn[11]`
1. `r learn[12]`
1. `r learn[13]`


## List the OHSU departments, centers and institutes of which you know that house experienced computational scientists

```{r, echo=FALSE, results='asis'}
n <- length(D[!is.na(OtherGroups), OtherGroups])
other <- D[!is.na(OtherGroups), OtherGroups][order(sample(1:n))]
```

1. `r other[1]`
1. `r other[2]`
1. `r other[3]`
1. `r other[4]`
1. `r other[5]`

## List the OHSU departments...

1. `r other[6]`
1. `r other[7]`
1. `r other[8]`
1. `r other[9]`

## List the OHSU departments...

1. `r other[10]`
1. `r other[11]`
1. `r other[12]`
1. `r other[13]`
